---
output: pdf_document
header-includes: \usepackage{dcolumn}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
packages <-  c("tidyverse",
               "reshape2",
               "nlme", "lme4",
               "data.table", "psych",
               "parallel","lubridate",
              "ggpubr", "broom", "table1", "apaTables", "psych", "stargazer", "corrplot", "tinytex")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```

Import Data
```{r}
plotting_data <- read.csv("/Volumes/devbrainlab/IndividualDifferencesMentalizing/IDMT_Data_Complete.csv")

demographics_data <- read.csv("/Volumes/devbrainlab/IndividualDifferencesMentalizing/NATE_PROLIFIC_COMPLETE.csv")

updated_plotting <- read.csv("/Volumes/devbrainlab/IndividualDifferencesMentalizing/withfluid.csv")
```

Demographics
```{r mylatextable1, results="asis"}

rejected_count <- table(demographics_data$status)
demographics_data <- demographics_data %>%
  filter(status=="APPROVED") %>%
  select("age", "Sex")

stargazer(demographics_data, nobs=FALSE,median=TRUE, omit.summary.stat = c("p25", "p75"))

```


Summary Stats
```{r mylatextable2, results = "asis"}
updated_plotting <- updated_plotting %>%
  select(-c("X", "participant_private_id","fluid_int", "keysar_score"))

stargazer(updated_plotting, type='latex', median=TRUE, nobs=FALSE, omit.summary.stat = c("p25", "p75"))

#updated_plotting[, 3:(ncol(plotting_data)-1)]
#column.labels = c("Good", "Better")
#stargazer(output, output2, type = "html", 
        #  title            = "These are awesome results!",
      #    covariate.labels = c("Temperature", "Wind speed", "Rain (inches)",
      #                         "2nd quarter", "3rd quarter", "Fourth quarter"),
      #    dep.var.caption  = "A better caption",
      #    dep.var.labels   = "Flight delay (in minutes)")
```


Function for resizing stargazer tables
```{r}
resizebox.stargazer = function(..., tab.width = "!", tab.height = "!"
                               ){
  #Activate str_which() function:
  require(stringr) 

  #Extract the code returned from stargazer()
  res = capture.output(
    stargazer::stargazer(...)
    )

  #Render the arguments:
  tab.width = tab.width
  tab.height = tab.height

  #Attach "}" between \end{tabular} and \end{table}
  res = 
    prepend(res, "}", before = length(res))

  #Input \resizebox before \begin{tabular}
  res = 
    c(res[1:str_which(res, "^\\\\begin\\{tabular\\}.*")-1],
      paste0("\\resizebox{",tab.width,"}{",tab.height,"}{%"),
      res[str_which(res, "^\\\\begin\\{tabular\\}.*"):length(res)]
      )

  #Produce the whole strings
  cat(res, sep = "\n")
}



#resizebox.stargazer(..., tab.width = "0.7\\textwidth")
```

Correlation Matrices

Corstars Function
```{r, echo=FALSE}

corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                     result=c("none", "html", "latex")){
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p <- correlation_matrix$P # Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .0001, "****", ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    "))))
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove last column and return the correlation matrix
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    if (result[1]=="none") return(Rnew)
    else{
      if(result[1]=="html") print(xtable(Rnew), type="html")
      else print(xtable(Rnew), type="latex") 
    }
}
```

corr code
```{r}
updated_plotting <- updated_plotting %>%
  rename(dot_alt_rt = dot_altercentric_interference, dot_ego_rt = dot_egocentric_interference, dot_alt_err = dot_altercentric_errors, dot_ego_err = dot_egocentric_errors, director_alt = director_altercentrism, director_ego = director_egocentrism)
#, keysar_ego = keysar_score
#viz <- updated_plotting %>%
 # select(director_alt, director_ego, dot_alt_rt, dot_ego_rt, dot_alt_err, dot_ego_err)

updated_plotting$dot_alt_err <- as.numeric(updated_plotting$dot_alt_err)
updated_plotting$dot_ego_err <- as.numeric(updated_plotting$dot_ego_err)

correlationmatrix <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err")])



#fluid int breaks this, possibly because of negative values


```
Table 3
```{r mylatextable3, results = "asis"}
#options(tinytex.verbose = TRUE)


#add , align = TRUE but currently breaks it (illegal character in array org)
#, rownames = TRUE, summary = FALSE
stargazer(correlationmatrix, align=TRUE)




#fullcorrelationmatrix <- cor(plotting_data[, !(colnames(plotting_data) %in% c("X", "participant_private_id", "six_nine"))])
#fluid int breaks this, possibly because of negative values
#stargazer(fullcorrelationmatrix)

```

Egocentrism & Altercentrism on Dot Task
```{r mylatextable4, results = "asis"}
table4 <- cor(updated_plotting[,c("dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err")])
stargazer(table4, align=TRUE)
```
Egocentricism & Altercentrism Across Tasks
```{r mylatextable5, results = "asis"}
table5 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err")])
stargazer(table5, align=TRUE)
```
Egocentrism & Altercentrism & MASC
```{r mylatextable6, results = "asis"}
table6 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "masc_accuracy", "masc_no_ment", "masc_over_ment", "masc_under_ment")])
stargazer(table6, align=TRUE, column.sep.width = "-8pt", font.size="tiny")

#likely needs 6/9
#column.sep.width = "-10pt",
```
Egocentrism/Altercentrism & Certainty/Uncertainty
```{r mylatextable7, results = "asis"}
table7 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "rfq_certainty", "rfq_uncertainty")])
stargazer(table7, align=TRUE,column.sep.width = "-8pt", font.size="tiny")
```
Fluid Intelligence & Mentalizing
```{r mylatextable8, results = "asis"}
table8 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "masc_accuracy", "masc_no_ment", "masc_over_ment", "masc_under_ment", "rfq_certainty", "rfq_uncertainty", "keysar_score", "fluid_int")])

stargazer(table8, align=TRUE,column.sep.width = "-8pt", font.size="tiny")

#(4 masc, 4 dot, 2 director, 2 rfq, 1 keysar score which I think we should call "ambiguous reference egocentrism") and the fluid intelligence score.

```
Self-reported psychopathology & Mentalizing
```{r mylatextable9, results = "asis"}
table9 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "masc_accuracy", "masc_no_ment", "masc_over_ment", "masc_under_ment", "rfq_certainty", "rfq_uncertainty", "keysar_score", "bsi_anxiety", "bsi_depression", "bsi_somatization", "pai_bor_affective_instability", "pai_bor_identity_problems", "pai_bor_negative_relationships", "pai_bor_self_harm", "pai_bor_total", "ders_awareness", "ders_clarity", "ders_goals", "ders_impluse", "ders_nonacceptance", "ders_strategies", "tpm_boldness", "tpm_disinhibition", "tpm_meanness", "tpm_total")])

stargazer(table9, align=TRUE,column.sep.width = "-8pt", font.size="tiny")

#all the mentalizing variables and the variables from the bsi-18, pai-bor, ders and tpm.
```
Psychopathology & Mentalizing
```{r mylatextable10, results = "asis"}
table10 <- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "tpm_boldness", "tpm_disinhibition", "tpm_meanness", "tpm_total")])
stargazer(table10, align=TRUE,column.sep.width = "-8pt", font.size="tiny")
```
Sense of Power, Agent/Patient perspective, social interaction anxiety, & mentalizing
```{r mylatextable11, results = "asis"}
table11<- cor(updated_plotting[,c("director_alt","director_ego", "dot_alt_rt","dot_ego_rt","dot_alt_err", "dot_ego_err", "sense_of_power", "pq_agent", "pq_recipient", "social_interaction_anxiety")])
stargazer(table11, align=TRUE,column.sep.width = "-8pt", font.size="tiny")

#can't find social anxiety
```
